---
title: "Quiz LAB-2 JP"
author: "Jp1212"
date: "2022-09-05"
output: html_document
runtime: shiny_prerendered
---
```{r setup, include=FALSE}
library(learnr)
```

````markdown

````
Question #1
```{r letter-a, echo=FALSE}
question("R was developed by statisticians working at?",
  answer("Microsoft"),
  answer("The University of Auckland",correct =TRUE),
  answer("Harvard University"),
  answer("Johns Hopkins University"),
   random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Error try again :c"
)
```
Question #2
```{r checkbox, echo = FALSE}
question_checkbox(
  "The definition of free software consists of four freedoms (freedoms 0 through 3). Which of the following is NOT one of the freedoms that are part of the definition?  Select all that apply.",
  
  answer("The freedom to redistribute copies so you can help your neighbor."),
  answer("The freedom to run the program, for any purpose."),
  answer("The freedom to study how the program works, and adapt it to your needs."),
  answer("The freedom to sell the software for any price.", correct = TRUE),
   answer("The freedom to restrict access to the source code for the software.", correct = TRUE),
   answer("The freedom to prevent users from using the software for undesirable purposes.", correct = TRUE),
   answer("The freedom to improve the program, and release your improvements to the public, so that the whole community benefits."),
  random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Be sure to select all toppings!"
)
```
Question #3
```{r checkbox-1, echo = FALSE}
question_checkbox(
  "In R the following are all atomic data types EXCEPT: (Select all that apply).",
  
  answer("Integer"),
  answer("Character"),
  answer("Complex"),
  answer("Array", correct = TRUE),
  answer("Logical"),
  answer("List", correct = TRUE ),
  answer("Table", correct = TRUE),
  answer("Data Frame", correct = TRUE),
  answer("Matrix",correct = TRUE),
  answer("Numeric"),
  random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Be sure to select all toppings!"
)
```
Question #4
```{r letter-o, echo=FALSE}
question("If I execute the expression x <- 4 in R, what is the class of the object `x' as determined by the `class()' function?",
  answer("Real"),
  answer("Numeric",correct =TRUE),
  answer("Vector"),
  answer("Integer"),
  answer("List"),
  answer("Complex"),
  answer("Matrix"),
  random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Error try again :c"
)
```
Question #5
```{r letter-Z, echo=FALSE}
question("What is the class of the object defined by the expression x   <- c(4,'a',TRUE)?",
  answer("Logical"),
  answer("Numeric"),
  answer("Integer"),
  answer("Mixed"),
  answer("Class"),
  answer("Character", correct = TRUE),
  random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Error try again :c"
)
```
Question #6
```{r letter-s, echo=FALSE}
question("If I have two vectors x <- c(1,3, 5) and y <- c(3, 2, 10), what is produced by the expression rbind(x, y)?",
  answer("a 3 by 2 matrix"),
  answer("a vector of length 3"),
  answer("a 2 by 2 matrix"),
  answer("a vector of length 2"),
  answer("a matrix with two column and three rows",correct = TRUE),
  answer("a 3 by 3 matrix"),
  random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Error try again :c"
)
```
Question #7
```{r letter-v, echo=FALSE}
question("A key property of vectors in R is that",
  answer("a vector cannot have have attributes like dimensions"),
  answer("elements of a vector can only be character or numeric"),
  answer("elements of a vector can be of different classes"),
  answer("the length of a vector must be less than 32,768"),
  answer("elements of a vector all must be of the same class",correct = TRUE),
  random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Error try again :c"
)
```
Question #8
```{r checkbox-3, echo = FALSE}
question_checkbox("Suppose I have a list defined as x <- list(2, a, b, TRUE). What does x[[2]] give me? Select all that apply.",
  answer("a list containing the number 2 and the letter 'a'."),
  answer("a list containing character vector with the letter 'a'."),
  answer("a character vector containing the letter 'a'.", correct = TRUE),
  answer("a character vector with the elements a and b."),
  answer("a character vector of length 1.", correct = TRUE),
  random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Be sure to select all toppings!"
)
```
Question #9
```{r letter-b, echo=FALSE}
question("Suppose I have a vector x <- 1:4 and a vector y <- 2. What is produced by the expression x + y?",
  answer("numeric vector with elements 1, 2, 3, 6."),
  answer("Aan integer vector with elements 3, 2, 3, 6."),
  answer("aa a numeric vector with elements 3, 2, 3, 6."),
  answer("is An integer vector with elements 3, 2, 3, 4."),
  answer("An integer vector with elements 3, 2, 3, 4."),
  answer ("A numeric vector with elements 3, 2, 3, 4."),
  answer ("Is a numeric vector with elements 3, 4, 5, 6", correct = TRUE),
  allow_retry = TRUE,
  try_again = "Error try again :c"
)
```
Question #10 
```{r checkbox-l, echo = FALSE}
question_checkbox("Suppose I have a vector x <- c(3, 5, 1, 10, 12, 6) and I want to set all elements of this vector that are less than 6 to be equal to zero. What R code achieves this? Select all that apply.",
  answer("x[x == 6] <- 0"),
  answer("x[x == 0] <- 6"),
  answer("x[x > 0] <- 6"),
  answer("x[x < 6] <- 0", correct = TRUE),
  answer("x[x > 6] <- 0"),
  answer ("x[x %in% 1:5] <- 0"),
  answer("x[x >= 6] <- 0"),
  answer ("x[x != 6] <- 0"),
  answer("x[x <= 5] <- 0"),
  answer("x[x == 0] < 6"),
  answer ("x[x < 6] == 0"),
  random_answer_order = TRUE,
  allow_retry = TRUE,
  try_again = "Be sure to select all toppings!"
)
```
Question #11

In the dataset provided for this Quiz, what are the column names of the dataset?

### Answer
Ozone, Solar.R, Wind, Temp, Month, Day

```R
install.packages("data.table")
library("data.table")
data <- fread('hw1_data.csv')
# Names Columns
names(data)
```

Question #12

Extract the first 2 rows of the data frame and print them to the console. What does the output look like?

### Answer
	  Ozone Solar.R Wind Temp Month Day
	1    41     190  7.4   67     5   1
	2    36     118  8.0   72     5   2

```R
# Two First Rows
data[c(1,2)]
```

Question #13

How many observations (i.e. rows) are in this data frame?

### Answer
153

```R
nrows(data)
```

Question #14

Extract the last 2 rows of the data frame and print them to the console. What does the output look like?

### Answer

	   Ozone Solar.R Wind Temp Month Day
	152    18     131  8.0   76     9  29
	153    20     223 11.5   68     9  30

```R
tail(data, 2)
```

Question #15

What is the value of Ozone in the 47th row?

### Answer
21

```R
data[47, Ozone]
```

Question #16

How many missing values are in the Ozone column of this data frame?

### Answer
37

```R
hw1 = read.csv('hw1_data.csv')
dub = subset(data, is.na(Ozone))
nrow(dub)

```

```R
# Remmove
data[complete.cases(data),]
```

Question #17

What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.

### Answer
42.1


```R
hw1 = read.csv('hw1_data.csv')
dub = subset(hw1, !is.na(Ozone), select = Ozone)
apply(dub, 2, mean) 
```

Question #18

Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?

### Answer
212.8

```R
data = read.csv('hw1_data.csv')
dub = subset(quiz_data, Ozone > 31 & Temp > 90, select = Solar.R)
apply(dub, 2, mean)
```

Question #19

What is the mean of "Temp" when "Month" is equal to 6?

### Answer
79.1

```R
data = read.csv('hw1_data.csv')
dub = subset(hw1, Month == 6, select = Temp)
apply(dub, 2, mean)
```

Question #20

What was the maximum ozone value in the month of May (i.e. Month = 5)?

### Answer
115


```R
data = read.csv('hw1_data.csv')
dub = subset(data, Month == 5 & !is.na(Ozone), select = Ozone)
apply(dub, 2, max)
```


